---
title: "The basics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tostada)
```

## Get started
The tostada package contains different types of useful functions to 
deal with asteorseismic data, both observational (e.g. light curves or 
observed oscillation spectra, etc.) and theoretical (e.g. structre models, 
synthetic oscillation spectra, etc.).

The complexity of asterosismic models (which different modeling options, 
parameters, physics, etc.) is superficially considered. Tosdata will just 
transform read data from file to a dataframe structured in a way it can be 
used by other functions of the package, i.e. for ploting purposes, and 
making it easy and robust, the compare different models.

## Types of functions
There are three types of funtions dependending on their functionality

  - Reading data (observations, models)
  - Seismic functions
  - Utilities
