---
title: "The basics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To get all the functionalities of tostada, just load the package as usual

```{r setup}
library(tostada)
```

The tostada package contains different types of useful functions to 
deal with asteorseismic data, both observational (e.g. light curves or 
observed oscillation spectra, etc.) and theoretical (e.g. structure models, 
synthetic oscillation spectra, etc.).



## Types of functions

There are three types of funtions dependending on their functionality

### Reading standard asteroseismic data

Tosdata will just transform read data from file to a dataframe structured in 
a way it can be used by other functions of the package, i.e. for ploting 
purposes, and making it easy and robust, the compare different models.

### Seismic functions

Tostada contains a set of frequently used functions that make use of tostada
structures (e.g. from reading observations/data). For example, l_sep() 
computes the large separation of a given theoretical spectrum read by any
of the read-type functions.

### Utilities (miscelanea)

Tostada includes a set of utilities related with asteroseismology that are
frequently necessary during asteroseismic data manipulation. An example of such
utility can be: constants(), which provide a dataframe with a set of constants
like the solar mass, solar radius, G, etc.
